The effects of binarity on planet occurrence rates measured by transit surveys

### 2018-01-30 paper/main.tex
minor edits

\paragraph{Ratio of searchable binaries to singles}
We must also specify the exact form of $\mu({\rm BF},M\a)$, the ratio of 
the number of searchable binary systems to singles.
Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
recall that the maximum searchable distance for singles and binaries are 
proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
Applying Equation~\ref{eq:N_searchable_prop},
\begin{equation}
\mu({\rm BF},M\a) = 
\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
f(q)\,\mathrm{d}q.
\label{eq:mu_general}
\end{equation}
If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
\propto q^\beta$, this simplifies to
\begin{equation}
\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
\left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q,
\label{eq:mu_power_laws}
\end{equation}
which can also be rewritten using the hypergeometric function.

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of 
        binary stars, in which the underlying volume-limited distribution is 
        uniform, qualitatively similar to
        Figure~16 of \citet{raghavan_survey_2010}.
        At a given observed transit depth, the searchable binaries in a 
        transit survey are magnitude-limited.
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}

This can be understood as a Malmquist bias: at fixed observed transit 
depth, for singles and primaries with the same luminosity, binaries are 
searchable to a greater distance;
In particular, the sample of searchable binaries is magnitude-limited.
Given a searchable binary, the probability that it has a mass ratio $q$ 
scales as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto 
(1+q^\alpha)^{3/2} q^\beta 
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the first term is the Malmquist bias when $L\propto M^\alpha$.
We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Figure~\ref{fig:q_distribn_mag_limited}.
In Monte Carlo simulations of transit surveys, it is 
important to draw binaries from a correctly biased mass-ratio distribution 
\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
    gunther_new_2017}.

@@

\section{Realistic Star and Planet Distributions}
\label{sec:more_complicated}
This section applies our general equation for the apparent rate 
density (Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in 
regimes of observational interest.
In what follows, we will write the rate density for each type of star, 
$\Gamma_i(r)$, as the product of a shape function and a constant:
\begin{equation}
\Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
\end{equation}
where $i=0$ corresponds to single stars, $i=1$ to primaries of 
binaries, and $i=2$ to secondaries of binaries.
The shape function is normalized to unity.
The $Z_i$'s are each system type's occurrence rate $\Lambda_i$, integrated 
over all planetary radii. In other words, they are number of planets per 
single, primary, or secondary star.
We want to consider the effects of varying not only $f_i(r)$ but also the
relative values of the $Z_i$'s.

@@

\subsubsection{Twin binaries}
We begin introducing realism by keeping all binaries as twins, but letting the 
planet radius distributions vary.
Specifically, we take
\begin{equation}
\Gamma_i(r) = Z_i f(r) = Z_i r^\delta/\mathcal{N}_r,
\end{equation}
for $f(r)$ the radius shape function, and $\mathcal{N}_r$ the shape function's 
normalization.
The resulting apparent rate density is 
\begin{equation}
\Gamma\a(r\a) = \frac{r\a^\delta}{\mathcal{N}_r} \left[
\frac{Z_0}{1+\mu}
+
2^{\frac{\delta+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
\right)
\right],
\label{eq:model5_apparent_rate_density}
\end{equation}
which is quite similar to the twin binary, fixed-planet case 
(Equation~\ref{eq:model_1_apparent_rate_density}), 
except for the radius dependence and normalization.
As in Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.
If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
density for singles becomes quite simple:
\begin{align}
\left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r}
&=
\frac{1 + 2^{\frac{\delta+3}{2}}\mu}{1 + \mu}.
\label{eq:power_law_correction}
\end{align}
If the binary fraction $0.1$, $\mu\approx 0.15$. Taking $\delta=-2.92$ from 
\citet{howard_planet_2012},  we get a correction factor $\Gamma\a/\Gamma_0 = 
1.004$.
In other words, the apparent rate density is an {\it over}estimate compared to 
the rate density of single stars, with a relative difference $\delta \Gamma_0 
= |\Gamma_0 - \Gamma\a | / \Gamma_0$ of 0.4\%.
This is quite a small effect!
Note though that it could change if the $Z_i$'s are not equal.
Also, the power law radius distribution $f(r) \propto r^\delta$ diverges for 
$\delta < 0$; \citet{howard_planet_2012}'s results indicate that this
approximation is good for $r\a\gtrsim 2r_\oplus$.
Similarly, it is nonsensical for $f(r)$ to be finite above some upper radius 
limit $r_u$, perhaps around $\approx 24r_\oplus$, based on the most inflated 
hot Jupiters.
An upper cut-off of $r_u$ would lead to smaller values of $\Gamma(r\a)$ 
down to $r_u/\sqrt{2}$, compared to an intrinsic power law without the cut-off.
We are not particularly interested in this effect; there are better 
models for hot Jupiter occurrence rates that we will discuss in 
Section~\ref{sec:further_models}.
If the assumptions behind this model (listed in 
Section~\ref{sec:general_formula}) are at all applicable in real transit surveys, 
this suggests that for $2r_\oplus \lesssim r\a \lesssim 17r_\oplus$, 
binarity's impact on derived occurrence rates is quite small.

@@

To check whether non-twin binaries change the preceding result, we now assume 
$f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the normalization.
This changes $\mu$ (Equation~\ref{eq:mu_general} simplifies to 
Equation~\ref{eq:mu_power_laws}).
It may also affect the rate density, which could be a function of the 
(varying) stellar mass.
Absorbing this dependence into a power law as well,
\begin{equation}
\Gamma_i(r,M) = Z_i \times \frac{r^\delta}{\mathcal{N}_r} \times
\frac{M^\gamma}{\mathcal{N}_M},
\end{equation}
where $Z_i$ is dimensionless, and the normalization constants carry 
the units (each side has units $[r^{-1} M^{-1}]$).
We assume that stars are a one-parameter family, given by $R \propto M \propto 
L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines everything 
about a secondary.

We are mostly interested in the apparent rate density's radius dependence.
Marginalizing Equation~\ref{eq:general_Gamma_a} over apparent stellar mass, we 
find
that when $Z_0=Z_1=Z_2$,
\begin{align}
X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r} \\
&=
\notag
\frac{1}{1+\mu}
\left[1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}\times 
\left(
\int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
\right.
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
\left.\left.
\int_0^1 {\rm d}q\,q^{\beta+\delta+\frac{5}{3}} 
(1+q^\alpha)^{\frac{3}{2}}
(1+q^{-\alpha})^{\frac{\delta+1}{2}}
\right)\right],
\label{eq:powerlaw_vary_binary}
\end{align}
where $\gamma$ does not appear because of the marginalization over $M\a$.
For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give 
$(\ldots)\approx 
1.50249$. %171211_model_integrals.nb
For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
relative difference between the apparent rate density and the rate density 
around singles is 4.8\%.
This indicates that considering only twin binaries gave us correct 
intuition: for a power-law radius distribution 
($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
number of planets orbiting singles, primaries, and secondaries, binarity 
influences apparent planet occurrence rates around Sun-like stars at the 
$\sim$few percent level.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Varying stars; broken power-law planet radius distribution}
\label{sec:model_3}

@@

Though the details of the true radius distribution $\Gamma_i(r)$ at 
$r<2r_\oplus$ are currently an active topic of research, we can consider how 
binarity affects this regime under different plausible assumptions.
For instance, assume that the true radius shape function is
\begin{align}
f(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus \\
{\rm constant} & \text{for } r\leq2r_\oplus.
\end{cases}
\right.
\label{eq:model3_radius_distribution}
\end{align}
As in the previous model, we assume that the observers know the true 
properties of all singles and primaries. The masses, radii, 
and luminosities of stars vary as $R \propto M \propto L^{\frac{1}{\alpha}}$.
Our ``nominal model'' remains the same: 
$\alpha=3.5$, $\beta=\gamma=0$, $\delta=-2.92$.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=\textwidth]{figures/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf}
    \caption{
        Fraction of detected planet at a given apparent planet radius coming 
        from singles (solid lines), primaries (dashed lines), and secondaries 
        (dotted lines).
        Three different values for $Z_2/Z_0$ are selected: $1$ (blue), $0.5$ 
        (orange), $0$ (green).
        The assumed true planet radius distribution is a broken power-law
        (Equation~\ref{eq:model3_radius_distribution}; same as 
        Figure~\ref{fig:occ_rate_model_3_log}).
    }
    \label{fig:frac_model_3}
\end{figure}

@@

\paragraph{The rate of Earth analogs}
In line with {\it Kepler}'s primary science goal, the rate of Earth-like 
planets orbiting Sun-like stars has been independently measured by 
\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
These efforts found that the one-year terrestrial planet occurrence rate 
is between $\approx\! 0.03$ and $\approx\!1$ per Sun-like star,
depending on assumptions that are made when calculating the
rate~\citep[see][, Figure~17]{burke_terrestrial_2015}.
In Section~\ref{sec:model_3}, our power law model indicates that when primaries, 
singles, and secondaries host the same number of planets, the apparent rate is 
50\% higher than the true rate around single stars.
Though this bias seems large, it is currently smaller than the other 
systematic factors that dominate the dispersion in $\eta_\oplus$ 
measurements.
If future analyses determine absolute values of $\eta_\oplus$ to 
better than a factor of two, binarity will likely merit closer attention.

@@

Ignoring these complications, in this work we concentrated on binarity's 
effects on star counts and the apparent radii of detected planets.
Assuming a power-law radius distribution, and that no secondaries host HJs,
our results from Section~\ref{sec:model_3} indicate that binarity 
could lead to underestimated HJ rates relative to singles by a multiplicative 
factor of at most $\approx 1.13$.
We later pointed out in Section~\ref{sec:further_models} that assuming a 
power-law radius distribution is probably wrong if one wishes to study the HJ 
rate discrepancy.
If we instead assumed a Gaussian radius 
distribution~\citep[following][]{petigura_CKS_2017}, apparent 
HJ rates are {\it greater} than the true rate around singles: the effect goes 
the wrong way.
\begin{comment}
If we believe the assumed power-law radius distribution, we can ask whether 
this ``correction factor'' might help resolve the discrepancy.
Explicitly, we ask: what is the probability of \citet{wright_frequency_2012}'s 
result, given a rate drawn from the stated bounds of~\citet{petigura_CKS_2017}?
In other words, we first take the true HJ rate per thousand stars as 
$\Lambda_{\rm HJ} = 5.7 \pm 1.3$, with Gaussian uncertainties. 
We then draw from a Poisson distribution and compute the probability of 
detecting at least 10 hot Jupiters in a sample of 836 stars.
Without accounting for binarity or metallicity, only 4\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account 
for~\citet{guo_metallicity_2017}'s measured metallicity difference between the 
{\it Kepler}\ field and the local solar neighborhood, 9\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply once more by $1.13$ to account for binarity's supposed bias, we 
find that 14\% of RV surveys would detect at least 10 hot Jupiters, still 
suggesting a weak discrepancy.

This suggestion should be taken with caution, because it (likely incorrectly) 
assumes a power-law radius distribution.
\end{comment}
The ``hot Jupiter island'' reported by~\citet{petigura_CKS_2017} cannot 
possibly be part of a continuous power law. 
Thus binarity is unlikely to resolve the HJ rate discrepancy.

@@

\paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
To apply this study to {\it Kepler}\ and other real
transit surveys, a few practical concerns become pressing.
One concern is that space-based missions with telemetric requirements
are often required to select target stars.
Even if the selection process is aimed at creating an SNR-limited
survey, as~\citet{batalha_selection_2010} did for {\it Kepler},
uncertainties about stellar parameters and on-sky instrument performance
can lead to deviations away from an SNR-limited stellar sample.

Further, in most transit surveys the detection efficiency is not
a step function in SNR.
Transit survey pipeline detection efficiencies are usually smooth
functions in SNR; see for example the injection \& recovery 
simulations 
performed by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, 
and the resulting smooth functional form adopted 
by~\citet{fulton_california-_2017}.
If we were to take a smooth detection probability in SNR, we would need to 
include a detection efficiency term in 
Equation~\ref{eq:apparent_rate_density} to inversely weight for planets 
with low probabilities of being detected.

The simplest way to avoid the conceptual complications of accounting for 
finite detection efficiency is to raise the SNR floor, to {\it e.g.,} 
${\rm SNR} \approx 12$ for {\it Kepler} 
(\citealt{fulton_california-_2017}, Figure~5).
To a good approximation, this allows one to use the boolean distinctions 
``searchable'' and ``not searchable'' for signals of an observed depth (at 
fixed orbital period).
This also makes the survey strictly SNR-limited, rather than ``fuzzily 
SNR-limited''.
Since the minimum SNR for detection is set in an arbitrary manner 
anyway\footnote{For example, {\it Kepler}'s threshold of ${\rm SNR}=7.1$ was 
set for there to be no more than one statistical false alarm across the full 
{\it Kepler} campaign~\citep{jenkins_tests_2002}. Equally valid would have 
been to insist on no more than $10^{-3}$ false alarms per survey, raising the 
detection floor.
}, this simplification would put occurrence rate studies on 
clearer conceptual 
ground, and facilitate the process of converting the observed distributions
of apparent radii into true radius distributions.

Finally, our calculations have ignored the fact that any given transit 
survey's finite SNR floor might censor the apparent rate density.
If the surveyed stars all have the same size, this is equivalent to 
saying that there might be a cutoff in apparent planet radii, below which no 
planets are detected.
The effects on our main results (e.g., 
Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:frac_model_3}, 
and~\ref{fig:gaussian_HJ}) would be that the apparent rate density 
below the cutoff in apparent radius would simply drop to zero.

@@

Assuming a broken power-law radius distribution, we showed in 
Figure~\ref{fig:frac_model_3} that there are many cases where a detected 
planet 
is much more likely to orbit the primary.
A planet orbiting the secondary does lead to extreme corrections.
However, at $r\a \gtrsim 2r_\oplus$, these cases are rare outliers.
At $r_\oplus \lesssim r\a \lesssim 2r_\oplus$, for all of the trial values of 
$Z_2/Z_0$ assumed in Figure~\ref{fig:frac_model_3}, a detected planet is 
always 
more likely to orbit the primary than the secondary.
Only at very small apparent radii, $r\a \approx 0.5r_\oplus$, and only if 
secondaries host as many planets as singles and primaries, does this ``rule'' 
break down.

>>>>

\paragraph{Ratio of searchable binaries to singles}
We must also specify the exact form of $\mu$, the ratio of 
the number of searchable binary systems to singles.
Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
recall that the maximum searchable distance for singles and binaries are 
proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
Applying Equation~\ref{eq:N_searchable_prop},
\begin{equation}
\mu({\rm BF},M\a) = 
\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
f(q)\,\mathrm{d}q.
\label{eq:mu_general}
\end{equation}
If the binary fraction is independent of $q$, $L \propto M^\alpha$, and $f(q) 
\propto q^\beta$, this simplifies to
\begin{equation}
\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
\left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q.
\label{eq:mu_power_laws}
\end{equation}
%which can also be rewritten using the hypergeometric function.
\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of 
        binary stars, in which the underlying volume-limited distribution is 
        uniform, qualitatively similar to
        Figure~16 of \citet{raghavan_survey_2010}.
        At a given observed transit depth, the searchable binaries in a 
        transit survey are magnitude-limited.
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}
This can be understood as a Malmquist bias: at fixed observed transit 
depth, for singles and primaries with the same luminosity, binaries are 
searchable to a greater distance;
In particular, the sample of searchable binaries is magnitude-limited.
Given a searchable binary, the probability that it has a mass ratio $q$ 
scales as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto 
(1+q^\alpha)^{3/2} q^\beta 
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the first term is the Malmquist bias when $L\propto M^\alpha$.
We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Figure~\ref{fig:q_distribn_mag_limited}.
In Monte Carlo simulations of transit surveys, it is 
important to draw binaries from a correctly biased mass-ratio distribution 
\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
    gunther_new_2017}.

@@

\section{Realistic Star and Planet Distributions}
\label{sec:more_complicated}
We now apply our general equation for the apparent rate 
density (Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in 
regimes of observational interest.
In what follows, we will write the rate density for each type of star, 
$\Gamma_i(r)$, as the product of a shape function and a constant:
\begin{equation}
\Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
\end{equation}
where $i=0$ corresponds to single stars, $i=1$ to primaries of 
binaries, and $i=2$ to secondaries of binaries.
The shape function is normalized to unity.
The $Z_i$'s are each system type's occurrence rate $\Lambda_i$, integrated 
over all planetary radii. In other words, they are number of planets per 
single, primary, or secondary star.
We want to consider the effects of varying not only $f_i(r)$ but also the
relative values of the $Z_i$'s.

@@

\subsubsection{Twin binaries}
We begin introducing realism by keeping all binaries as twins, but letting the 
planet radius distributions vary.
First, we assume a power law,
\begin{equation}
\Gamma_i(r) = Z_i f(r) = Z_i r^\delta/\mathcal{N}_r,
\end{equation}
for $f(r)$ the radius shape function, and $\mathcal{N}_r$ the shape function's 
normalization.
The resulting apparent rate density is 
\begin{equation}
\Gamma\a(r\a) = \frac{r\a^\delta}{\mathcal{N}_r} \left[
\frac{Z_0}{1+\mu}
+
2^{\frac{\delta+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
\right)
\right],
\label{eq:model5_apparent_rate_density}
\end{equation}
which is quite similar to the twin binary, fixed-planet case 
(Equation~\ref{eq:model_1_apparent_rate_density}), 
except that the radius dependence and normalization are different.
As in Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.
If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
density for singles becomes quite simple:
\begin{align}
\left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r}
&=
\frac{1 + 2^{\frac{\delta+3}{2}}\mu}{1 + \mu}.
\label{eq:power_law_correction}
\end{align}
If the binary fraction is $0.1$, $\mu\approx 0.15$. Taking $\delta=-2.92$ from 
\citet{howard_planet_2012},  we get a correction factor $\Gamma\a/\Gamma_0 = 
1.004$.
In other words, the apparent rate density is an {\it over}estimate compared to 
the rate density of single stars, with a relative difference $\delta \Gamma_0 
= |\Gamma_0 - \Gamma\a | / \Gamma_0$ of 0.4\%.
This is quite a small effect!
Clearly though, it cannot apply at small radii, since $f(r) \propto r^\delta$ 
diverges; \citet{howard_planet_2012}'s 
results indicate that the power law planet radius distribution holds for 
$r\a\gtrsim 2r_\oplus$.
It is similarly nonsensical for $f(r)$ to be finite above some upper radius 
limit $r_{\rm u}$, perhaps around $\approx 24r_\oplus$, based on the most 
inflated hot Jupiters.
An upper cut-off of $r_{\rm u}$ would lead to smaller values of $\Gamma(r\a)$ 
down to $r_{\rm u}/\sqrt{2}$, compared to an intrinsic power law without the 
cut-off.
We are not particularly interested in this effect because there are better 
models for hot Jupiter occurrence rates that we will discuss in 
Section~\ref{sec:further_models}.
If the assumptions behind this model are at all applicable to real transit 
surveys, Equation~\ref{eq:power_law_correction} suggests that for $2r_\oplus 
\lesssim r\a \lesssim 17r_\oplus$, binarity's impact on apparent occurrence 
rates is quite small.

@@

To check whether non-twin binaries change the preceding result, we now assume 
$f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the normalization.
This changes $\mu$ (Equation~\ref{eq:mu_general} simplifies to 
Equation~\ref{eq:mu_power_laws}).
It may also affect the rate density, which could be a function of the 
varying stellar mass.
Absorbing this dependence into a power law as well,
\begin{equation}
\Gamma_i(r,M) = Z_i \times \frac{r^\delta}{\mathcal{N}_r} \times
\frac{M^\gamma}{\mathcal{N}_M},
\end{equation}
where $Z_i$ is dimensionless, and the normalization constants carry 
the units (each side has units $[r^{-1} M^{-1}]$).
We assume that stars are a one-parameter family, given by $R \propto M \propto 
L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines everything 
about a secondary.

We are mostly interested in the apparent rate density's radius dependence.
Marginalizing Equation~\ref{eq:general_Gamma_a} over apparent stellar mass, we 
find
that when $Z_0=Z_1=Z_2$,
\begin{align}
X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r} \\
&=
\notag
\frac{1}{1+\mu}
\left[1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}\times 
\left(
\int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
\right.
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
\left.\left.
\int_0^1 {\rm d}q\,q^{\beta+\delta+\frac{5}{3}} 
(1+q^\alpha)^{\frac{3}{2}}
(1+q^{-\alpha})^{\frac{\delta+1}{2}}
\right)\right],
\label{eq:powerlaw_vary_binary}
\end{align}
where $\gamma$ does not appear because of the marginalization over $M\a$.
For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give 
$(\ldots)\approx 
1.50249$. %171211_model_integrals.nb
For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
relative difference between the apparent rate density and the rate density 
around singles is 4.8\%.
This indicates that considering only twin binaries gave us correct 
intuition: for a power law radius distribution 
($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
number of planets orbiting singles, primaries, and secondaries, binarity 
influences apparent planet occurrence rates around Sun-like stars at the 
$\sim$few percent level.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Varying stars; broken power law planet radius distribution}
\label{sec:model_3}

@@

Though the details of the planet radius distribution $\Gamma_i(r)$ at 
$r<2r_\oplus$ are currently an active topic of research, we can consider how 
binarity affects this regime under different plausible assumptions.
For instance, assume that the true radius shape function is
\begin{align}
f(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus \\
{\rm constant} & \text{for } r\leq2r_\oplus.
\end{cases}
\right.
\label{eq:model3_radius_distribution}
\end{align}
As in the previous model, we presume that the observers know the true 
properties of all singles and primaries. The masses, radii, 
and luminosities of stars vary as $R \propto M \propto L^{\frac{1}{\alpha}}$.
Our ``nominal model'' remains the same: 
$\alpha=3.5$, $\beta=\gamma=0$, $\delta=-2.92$.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=\textwidth]{figures/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf}
    \caption{
        Fraction of detected planet at a given apparent planet radius coming 
        from singles (solid lines), primaries (dashed lines), and secondaries 
        (dotted lines).
        Three different values for $Z_2/Z_0$ are selected: $1$ (blue), $0.5$ 
        (orange), $0$ (green).
        The assumed true planet radius distribution is a broken power law
        (Equation~\ref{eq:model3_radius_distribution}; same as 
        Figure~\ref{fig:occ_rate_model_3_log}).
    }
    \label{fig:frac_model_3}
\end{figure}

@@

\paragraph{The rate of Earth analogs}
In line with {\it Kepler}'s primary science goal, the rate of Earth-like 
planets orbiting Sun-like stars has been independently measured by 
\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
These efforts found that the one-year terrestrial planet occurrence rate 
is between $\approx\! 0.03$ and $\approx\!1$ per Sun-like star,
depending on assumptions that are made when calculating the
rate~\citep[see][Figure~17]{burke_terrestrial_2015}.
In Section~\ref{sec:model_3}, our power law model indicates that when 
primaries, 
singles, and secondaries host the same number of planets, the apparent rate is 
50\% higher than the true rate around single stars.
Though this bias seems large, it is currently smaller than the other 
systematic factors that dominate the dispersion in $\eta_\oplus$ 
measurements.
If future analyses determine absolute values of $\eta_\oplus$ to 
better than a factor of two, binarity will likely merit closer attention.

@@

Ignoring these complications, in this work we concentrated on binarity's 
effects on star counts and the apparent radii of detected planets.
Assuming a power law radius distribution, and that no secondaries host HJs,
our results from Section~\ref{sec:model_3} indicate that binarity 
could lead to underestimated HJ rates relative to singles by a multiplicative 
factor of at most $\approx 1.13$.
We later pointed out in Section~\ref{sec:further_models} that assuming a 
power law radius distribution is probably wrong if one wishes to study the HJ 
rate discrepancy.
If we instead assumed a Gaussian radius 
distribution~\citep[following][]{petigura_CKS_2017}, apparent 
HJ rates are {\it greater} than the true rate around singles: the effect goes 
the wrong way.
\begin{comment}
If we believe the assumed power law radius distribution, we can ask whether 
this ``correction factor'' might help resolve the discrepancy.
Explicitly, we ask: what is the probability of \citet{wright_frequency_2012}'s 
result, given a rate drawn from the stated bounds of~\citet{petigura_CKS_2017}?
In other words, we first take the true HJ rate per thousand stars as 
$\Lambda_{\rm HJ} = 5.7 \pm 1.3$, with Gaussian uncertainties. 
We then draw from a Poisson distribution and compute the probability of 
detecting at least 10 hot Jupiters in a sample of 836 stars.
Without accounting for binarity or metallicity, only 4\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account 
for~\citet{guo_metallicity_2017}'s measured metallicity difference between the 
{\it Kepler}\ field and the local solar neighborhood, 9\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply once more by $1.13$ to account for binarity's supposed bias, we 
find that 14\% of RV surveys would detect at least 10 hot Jupiters, still 
suggesting a weak discrepancy.

This suggestion should be taken with caution, because it (likely incorrectly) 
assumes a power law radius distribution.
\end{comment}
The ``hot Jupiter island'' reported by~\citet{petigura_CKS_2017} cannot 
possibly be part of a continuous power law. 
Thus binarity is unlikely to resolve the HJ rate discrepancy.

@@

\paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
To apply this study to real transit surveys, a few practical concerns become 
pressing.
One concern is that space-based missions with telemetric requirements
are often required to select target stars.
Even if the selection process is aimed at creating an SNR-limited
survey, as~\citet{batalha_selection_2010} did for {\it Kepler},
uncertainties in stellar parameters and the modeled instrument performance
can lead to deviations away from an SNR-limited stellar sample.

Further, in most transit surveys the detection efficiency is not
a step function in SNR.
Transit survey pipeline detection efficiencies are usually smooth
functions in SNR; see for example the injection-recovery 
simulations 
performed by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, 
and the resulting smooth detection efficiency adopted 
by~\citet{fulton_california-_2017}.
If we were to assume a smooth detection probability in SNR, we would need to 
include a detection efficiency term in 
Equation~\ref{eq:apparent_rate_density} to inversely weight for planets 
with low probabilities of being detected.

The simplest way to avoid the conceptual complications of accounting for 
finite detection efficiency is to raise the SNR floor, to {\it e.g.,} 
${\rm SNR} \approx 12$ for {\it Kepler} 
(\citealt{fulton_california-_2017}, Figure~5).
To a good approximation, this allows one to use the boolean distinctions 
``searchable'' and ``not searchable'' for signals of an observed depth (at 
fixed orbital period).
By making the survey strictly SNR-limited, rather than ``fuzzily 
SNR-limited'', binarity's effects become much easier to model.
Since the minimum SNR for detection is set in an arbitrary manner 
anyway\footnote{For example, {\it Kepler}'s threshold of ${\rm SNR}=7.1$ was 
set for there to be no more than one statistical false alarm across the full 
{\it Kepler} campaign~\citep{jenkins_tests_2002}. Equally valid would have 
been to insist on no more than $10^{-3}$ false alarms per survey, raising the 
detection floor.
}, this simplification would put occurrence rate studies on 
clearer conceptual 
ground, and facilitate the process of converting the observed distributions
of apparent radii into true radius distributions.

Finally, our calculations also ignore the fact that any given transit 
survey's finite SNR floor might censor the apparent rate density.
If the surveyed stars all have the same size, this is equivalent to 
saying that there might be a cutoff in apparent planet radii, below which no 
planets are detected.
The effects on our main results (e.g., 
Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:frac_model_3}, 
and~\ref{fig:gaussian_HJ}) would be that the apparent rate density 
below the cutoff in apparent radius would simply drop to zero.

@@

Assuming a broken power law radius distribution, we showed in 
Figure~\ref{fig:frac_model_3} that there are many cases where a detected 
planet 
is much more likely to orbit the primary.
A planet orbiting the secondary does lead to extreme corrections.
However, at $r\a \gtrsim 2r_\oplus$, these cases are rare outliers.
At $r_\oplus \lesssim r\a \lesssim 2r_\oplus$, for all of the trial values of 
$Z_2/Z_0$ assumed in Figure~\ref{fig:frac_model_3}, a detected planet is 
always 
more likely to orbit the primary than the secondary.
Only at very small apparent radii, $r\a \approx 0.5r_\oplus$, and only if 
secondaries host as many planets as singles and primaries, does this ``rule'' 
break down.
